---
title: "Prediction Assignment Writeup"
author: "Hanif Noer Rofiq"
date: '2022-03-14'
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
#install.packages('caret')
#install.packages('rpart.plot')
#install.packages('randomForest')
```

## Background

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement -- a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: <http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har> (see the section on the Weight Lifting Exercise Dataset).

## Data

The training data for this project are available here:

<https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv>

The test data are available here:

<https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv>

The data for this project come from this source: <http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har>. If you use the document you create for this class for any purpose please cite them as they have been very generous in allowing their data to be used for this kind of assignment.

### Data Processing

Load data and library

```{r Load Library}
library(lattice)
library(caret)
library(rpart)
library(rpart.plot)
library(randomForest)
library(ggplot2)
```

```{r Load Data}
set.seed(22)
train <-"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
test <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
trainDF <- read.csv(train, na.strings=c("NA","#DIV/0!", ""))
testDF  <- read.csv(test, na.strings=c("NA","#DIV/0!", ""))

```

### Data Cleansing

First, let see the data we have

```{r}
summary(trainDF)
```

```{r}
#summary(testDF)
```

Then, we remove columns that contain missing values (NA)
```{r}
trainDF<-trainDF[,colSums(is.na(trainDF)) == 0]
testDF <-testDF[,colSums(is.na(testDF)) == 0]
```

```{r}
#names(trainDF)
#sum(is.na(testDF))
```

and we remove unnecessary columns
```{r}
trainDF   <-trainDF[,-c(1:7)]
testDF <-testDF[,-c(1:7)]
```

```{r}
names(trainDF)
```

### Cross-Validation

This step divides the training data into a training set and cross validation set for 80-20
```{r}
newtrainDF <- createDataPartition(y=trainDF$classe, p=0.8, list=FALSE)
traintdf <- trainDF[newtrainDF, ] 
testtdf <- trainDF[-newtrainDF, ]
```


### Predicition using Random Forest

I'm using random forest because based on [my experience] (<https://www.kaggle.com/hanifnoerrofiq>), the result of random forest is better than other ordinary algorithms

```{r}
traintdf$classe = factor(traintdf$classe)
rf <- randomForest(classe ~. , data=traintdf, method="class")
rf_result <- predict(rf, traintdf, type = "class")
rf_result2 <- predict(rf, testtdf, type = "class")
```

```{r}
confusionMatrix(rf_result, as.factor(traintdf$classe))
```
Looks like our model give excellent result, but we need to cross validate the performance to avoid over fitting. Let see how our model performs with the cross validation set.
```{r}
confusionMatrix(rf_result2, as.factor(testtdf$classe))
```
The accuracy is 99.5% which is excellent and the expected out-of-sample error is estimated at 0.5%

### Submission
Applying our machine learning algorithm to the 20 test cases available in the test data above.
```{r}
submission <- predict(rf, testDF, type="class")
submission
```
